%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.35 in,right=0.4 in,bottom=0.3in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jigar Chavada}
\address{GitHub: https://github.com/jigar3 \\ LinkedIn: https://www.linkedin.com/in/jsc39}
\address{Room No. 1329, BH-4, IIIT Allahabad}
\address{+91 9594881428 \\ Chavada.Jigar.3@gmail.com}






\begin{document}  

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{ B.Tech in Electronics \& Communication Engineering, \textbf{IIIT Allahabad} } \hfill {2017-2021}
\\
{ XII Standard  , \textbf{IDUBS College, Mumbai} , Percentage: 86.92\%} \hfill {2014-2016}
\\
{ X Standard  , \textbf{SBM Padwal Vidyalaya, Mumbai} , Percentage: 93.2\%}  \hfill {2014}
\end{rSection} 


\begin{rSection}{ Work Experience } \itemsep -1pt        

\begin{rSubsection}{ByodBuzz: Python Development Intern}{April 2018 - July 2018}{}    

\vspace{-3pt}

\item Implemented various scripts for Web Scraping \& Automation using Python.
\item Worked with frameworks \& technologies such as BeautifulSoup, Seleniuim, AWS.
\end{rSubsection} 

\vspace{-4pt}

 
\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Skills} \itemsep -3pt  

{\textbf{Development Languages:} JavaScript, Python, C, Golang, Shell Scripting }  
\\
{\textbf{Frameworks \& Technologies:} ReactJs, VueJs, Express, TypeScript, Redux, MongoDB, MySQL, Flask }
\\
{\textbf{Tools \& Platforms:} Arch Linux, Ubuntu, VS Code, Postman, Git }
\end{rSection}  

%	PROJECTS

\begin{rSection}{PROJECTS}

%------------------------------------------------

\begin{rSubsection}{Wall Street}
{IIIT Allahabad}{}{}

\vspace{-3pt}

\item Made a Full Stack web application which allows one to trade on NASDAQ using virtual money.
\item The Frontend was designed using React with static typing checking implemented via TypeScript and used Redux for State Management inside the application.
\item Express Server with MongoDB as the database powered the backend. Authentication and Security was done using JWT.

\end{rSubsection}

%--------------------------------------------------------------------------------------------------

\begin{rSubsection}{Blogging Application}
{IIIT Allahabad}{}

\vspace{-3pt}

\item Implemented a simple Blogging Application with a Go based backend \& VueJs frontend
\item Gin Web Framework was used to implement the backend service with Mongo based database.
 
\end{rSubsection} 
\end{rSection} 


% POSITION OF RESPONSIBILITY
%-----------------------------------------------------------------------------
  
\begin{rSection}{POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Core Team Member}{August 2018 - October-2018}{Effervescence'18, IIIT Allahabad}{}              
\item Worked in a team of 35 people to organise Effervescence'18, annual cultural fest of IIIT Allahabad.
\item Part of the Sponsorship \& Branding Departments of the fest. 
\end{rSubsection}  


\begin{rSubsection}{Member}{April 2018 - Present}
{Web Development Wing, GeekHaven, IIIT Allahabafd}{}
\item Conducting Workshops for freshers related to Web Technologies and motivate them to learn and create projects of their own. 
\end{rSubsection}  

\end{rSection}


%--------------------------------------------------------------------------------------
% Awards & Honors
%--------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Honors} \itemsep -2pt   

\begin{itemize}
 
\item Runners Up at Headout Sponsored \textbf{Prototype Hackathon} in IIIT Allahabad \hfill October 2018 
\item Winner \textbf{Opencode'18}, a one month long Open Source Competition wherein participants solves issues in various opensource projects, organised by GeekHaven, IIIT Allahabad \hfill February 2018
\end{itemize}  


\end{rSection} 

\end{document}